Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-05-04 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
minor changes

		Faint, high-temperature emission in active region cores has long been predicted as a signature of nanoflare heating. However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity. This second paper in our series on hot non-flaring plasma in active regions aims to show how the assumption of electron-ion equilibrium leads to misleading conclusions regarding the hot emission. We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies. By computing the emission measure distributions and calculating their ``hotward'' slopes, we have concluded that not treating the electron and ion populations separately leads to a mischaracterization of the hot emission. Additionally, we find that, while emission due to separate electron and ion heating differs greatly hotward of the peak, the respective coolward emission measure slopes are similar such that a distinction between the heating of one species over another based on this criteria alone is not possible. 

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions. \hl{Are we going to look at the single-fluid case? If not, remove if here and reconsider total number of heating functions.}}

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0$ is $H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 

>>>>

		Faint, high-temperature emission in active region cores has long been predicted as a signature of nanoflare heating. However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity. In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure di . We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies. By computing the emission measure distributions and calculating their ``hotward'' slopes, we have concluded that not treating the electron and ion populations separately leads to a mischaracterization of the hot emission. Additionally, we find that, while emission due to separate electron and ion heating differs greatly hotward of the peak, the respective coolward emission measure slopes are similar such that a distinction between the heating of one species over another based on this criteria alone is not possible. 

@@

		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions. \hl{Are we going to look at the single-fluid case? If not, remove if here and reconsider total number of heating functions.}}

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 
